Model Finding for Recursive Functions in SMT

### 2015-04-29 tex/main.tex
more

@@

Alloy (and Alloy idiom by Kuncak \& Jackson), Kodkod
The model finder for KIV based on Alloy
Nitpick
Leon

@@

>>>>

  * corecursive functions???
    * productive

@@

Alloy (and Alloy idiom by Kuncak \& Jackson), Kodkod

The model finder for KIV based on Alloy

Refute
  * unsound handling of datatypes

Nitpick
  * inductive / coinductive predicates
  * quotient types

Leon

@@

  * future work
    * (co)inductive predicates

{%\footnotesize
\def\ackname{Acknowledgment}
\paragraph{%\footnotesize
\ackname.}

This research is partially supported by the Inria technological development
action \relax{Contrexemples Utilisables par Isabelle et Coq} (CUIC).

}
